\documentclass[11pt, letterpaper]{report}
\input{../../preamble.tex}
\usepackage{titlepageBU}
\title{Modern Algebra 1}
\date{09/26/24}
\courseID{MA 541}
\professor{Dr. Duque-Rosero}
\courseSection{A1}
\renewcommand{\mod}[1]{\;(\text{mod}\;#1)}
\begin{document}
\makeproblem
\section*{Problem 1}
\begin{solution}
	For convenience, let $I$ always denote the $2\times 2$ identity matrix within this problem, and let $H\coloneqq \left\{ \alpha I  \mid \alpha \in\mathbb{Z}_n \land \alpha ^2\not\equiv0\mod{n}\right\} $.

	First, we show that $H\subseteq Z(\operatorname{GL}_2(\mathbb{Z}_n)) $. Let $A \in \operatorname{GL}_2(\mathbb{Z}_n) $, and let $\alpha \in\mathbb{Z}_n$. It follows that
	\[
		(\alpha I)A=\alpha (IA)=\alpha A=A\alpha =(AI)\alpha =A(I\alpha )=A(\alpha I)
	.\]
	Thus, for all $A\in \operatorname{GL}_2(\mathbb{Z}_n) $, $\alpha IA=A\alpha I$. Therefore, $H\subseteq Z(\operatorname{GL}_2(\mathbb{Z}_n)) $.

	Before we show the converse, I have some commentary on the problem. The first line of the problem states $\operatorname{GL}_2(\mathbb{Z}_n) $ is a group for $n\geq 2$. After a lot of confusion, it turns out $\operatorname{GL}_2(\mathbb{Z}_n) $ is only a group for $n$ a prime integer. This is fairly easy to prove. Let $A,B\in \operatorname{GL}_2(\mathbb{Z}_n) $. Then $\operatorname{GL}_2(\mathbb{Z}_n) $ is a group if and only if $AB\in \operatorname{GL}_2(\mathbb{Z}_n) $. I leae it as an exercise to prove the other requirements for a group, but they will be satisfied for any $n$. For any integer $0<a<n$, we can very easily construct a matrix $A$ such that $\left| A \right| =a$. Let $0<a,b<n$, and let $\left| A \right| =a$ an $\left| B \right| =b$. We thus have $\det (AB)=ab$. Therefore, $AB\in \operatorname{GL}_2(\mathbb{Z}_n) $ if and only if $ab\not\equiv 0\mod{n}$. For any $n$ not prime, there exist $a,b\in\mathbb{Z}$ such that this statement is false. Therefore, $n$ must be prime. The conclusion of all this is that the set being over $\mathbb{Z}_n$ literally doesn't matter and this should be provable via normal matrix algebra.

Now, we show the converse. 
\end{solution}
\section*{Problem 2}
\begin{solution}
	This was easy, in fact we did an example of this last homework. Let $G=\left\{ e,a,b,c \right\} $ be a group with identity $e$. Let $a^2=b^2=c^2=e$, and let $ab=ba=c$. It follows that $bc=cb=a$ and $ac=ca=b$. We give the following Cayley table to help with this visualization.
	\begin{center}
	\begin{tabular}{c|cccc}
		$\cdot $ &$e$ &$a$ &$b$ &$c$ \\
		\hline
		$e$ &$e$&$a$&$b$&$c$\\
		$a$ &$a$&$e$&$c$&$b$\\
		$b$ &$b$&$c$&$e$&$a$\\
		$c$ &$c$&$b$&$a$&$e$
	\end{tabular}
	\end{center}
	A great example of an equivalent group up to isomorphism is the subgroup $\left\{ R_0,R_{180},S,R_{180}S \right\} $ of the dihedral group $D_n$ for an even integer $n$.

	The group is clearly not cyclic. It has 4 elements, none of which generate the group. Since $a^2=b^2=c^2=e$, we have
	\[
		\left<a \right> = \left\{ e,a \right\} 
	,\]
	\[
		\left<b \right> =\left\{ e,b \right\} 
	,\]
	\[
		\left<c \right> =\left\{ e,c \right\} 
	.\]
	Therefore, the set is not cyclic. Additionally, these sets and the set $\left\{ e \right\} $ are the only possible cyclic subgroups of $G$, which is obvious since they are the sets generated by each element of $G$. It remains to be shown no other subgroups of $G$ exist.

	Let $H\subsetneq G$ have more than 2 elements. Since any set must have the identity element in it, we have already seen all the subgroups of $G$ with 2 or less elements. They are exactly the cyclic subgroups of $G$. We must only consider sets with more than 2 but less than 4 elements. In other words, we must consider sets with only 3 elements. All of these sets, in order to be groups, must have the identity element, so they must have exactly 2 non-identity elements $a $, $b$, or $c$ in them. Since $ab=ba=c$, $bc=cb=a$, and $ca=ac=b$, none of these sets would be closed under group multiplication. Thus, there exist no proper subgroups of $G$ other than the cyclic subgroups.
\end{solution}
\section*{Problem 3}
\begin{solution}
	
\end{solution}
\section*{Problem 4}
\begin{solution}
	Let $G$ be a group with identity $e$. Let $a,b\in G$ such that $\left| a \right| =n$, $\left| b \right| =m$, and $\operatorname{gcd}(n,m) =1$.

	Let there exist some $g\in \left<a \right>$ such that $g\in \left<b \right>$. Since $g\in \left<a \right>$, there must exist some $k\in\mathbb{Z}$ such that $g=a^k$. Since $\left<b \right>$ is a group and thus closed under multiplication, any power of $a^k$ must be an element of $\left<b \right>$. Thus, we have
	\[
		\left<a^k \right>\subseteq \left<b \right>
	.\]
	By the fundamental theorem of cyclic subgroups, we know that $\left| \left<a^k \right> \right| $ will divide $m$. Additionally, by the same logic $\left<a^k \right>\subseteq \left<a \right>$, so $\left| \left<a^k \right> \right| $ must also divide $n$. Since $m$ and $n$ are relatively prime, the only number that divides both $m$ and $n$ is $1$, and thus $\left| \left<a^k \right> \right| =1$. It follows from this that
	\[
		\left( a^k \right) ^1=e
	.\]
	Thus,
	\[
		a^k=e
	.\]
	Therefore, $g\in \left<a \right>$ and $g\in \left<b \right>$ implies $g=e$. This should suffice to show $\left<a \right>\cap \left<b \right> = \left\{ e \right\} $.
\end{solution}
\section*{Problem 5}
\begin{solution}
	Let $a\in G$. The set $C(a)$ is the set of all $g\in G$ such that $ga=ag$. We need only show $\left<a \right>\subseteq C(a)$. Since $a^k\in \left<a \right>$ for any $k\in\mathbb{Z}$, we have
	\[
		a\left( a^k \right) =a\left( a^{k-1}a \right) =\left( aa^{k-1} \right) a=a^{k}a
	.\]
	Therefore, for any $a^k\in \left<a \right>$, $a^ka=aa^k$. Thus, $\left<a \right>\subseteq C(a)$.
\end{solution}
\end{document}
