\documentclass[11pt, letterpaper]{report}
\input{../../preamble.tex}
\usepackage{titlepageBU}
\title{Honors Differential Equations}
\date{09/06/24}
\courseID{MA 231}
\professor{Dr. C. Eugene Wayne}
\courseSection{A1}
\begin{document}
 \makeproblem
 \begin{enumerate}
	 \item Please write your name, semester at BU, and anticipated major.\par
	 Grant Talbert - 1st Semester - Double major in math \& physics
 	 \item Write a paragraph describing your mathematics background. (For example, what was your calculus course like? What are your main memories from multi-dimensional calculus?). Please be sure to use complete sentences and correct grammar and spelling.\par
		 I've taken calculus 1\&2 twice at this point; I failed Calculus AB/BC in high school, mostly due to depression, and retook it at a community college which made it fairly easy. After that, I took Multivariable Calculus, Linear Algebra, and self-studied about half of the Modern Algebra 1 curriculum. I believe I have a fairly solid mathematical foundation, and incase I get lost on content from a previous class, I take fairly detailed notes that I can look back on at anytime.
	 \item In a couple of sentences, please tell me why you decided to take MA 231 instead of MA 226.\par
	 Most people I've met who have taken this class cite the smaller class size as their main reason, but to me that's just an added benefit. But I personally took the class because the extra material looked very interesting, and I generally enjoy doing math so I don't mind the extra work that comes with it.
 \end{enumerate}
\end{document}
